working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
EDITS

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6,fig.cap="A"}

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=3,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species coloured by family."}

### 2019-03-05 Manuscript_draft/Manuscript_draft.tex
EDITS

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{Average effect size and confidence intervals (95\%) of the 9
heterospecific treatments of 50\% pollen to the different 10 focal
species}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{Average effect size and confidence intervals (95\%) of the 9
heterospecific treatments of 50\% pollen to the different 10 focal
species coloured by family.}
\end{figure}
